---
title: "Introduction to the randgeo package"
author: "Scott Chamberlain"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: readable
vignette: >
  %\VignetteIndexEntry{Introduction to the randgeo package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE}
library("knitr")
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL,
            x[lines],
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

`randgeo` is a no dependency R package for generating random lat/long positions, or
random WKT or GeoJSON points or polygons.

The benefit of no dependencies is that it can easily be used in other packages 
without any pain.

This package is adapted from Javascript's <https://github.com/tmcw/geojson-random>

## Install

Stable `randgeo` version from CRAN

```{r eval=FALSE}
install.packages("randgeo")
```

Or, the development version from Github

```{r eval=FALSE}
devtools::install_github("ropensci/randgeo")
```

```{r}
library("randgeo")
```

## random position

```{r}
rg_position()
```

Many positions

```{r}
rg_position(10)
```

Random position within a bounding box

```{r}
rg_position(bbox = c(50, 50, 60, 60))
```

## Well-known text

### random points

A single point

```{r}
wkt_point()
```

Many points

```{r}
wkt_point(count = 10)
```

Within a bounding box

```{r}
wkt_point(bbox = c(50, 50, 60, 60))
```

The `fmt` parameter controls how many decimal points

```{r}
wkt_point()
wkt_point(fmt = 10)
```


### random polygons

```{r}
wkt_polygon()
```

Adjust number of vertices (Default: 10)

```{r}
wkt_polygon(num_vertices = 4)
```

Adjust maximum number of decimal degrees latitude or longitude that a 
vertex can reach out of the center of the Polygon (Default: 10)

```{r}
wkt_polygon(max_radial_length = 5)
```

Within a bounding box

```{r}
wkt_polygon(bbox = c(-130, 50, -120, 60))
```



## GeoJSON

### random points

A single point

```{r}
geo_point()
```

Many points

```{r output.lines=1:10}
geo_point(count = 10)
```

Within a bounding box

```{r}
geo_point(bbox = c(50, 50, 60, 60))
```


### random polygons

```{r}
geo_polygon()
```

Adjust number of vertices (Default: 10)

```{r}
geo_polygon(num_vertices = 4)
```

Adjust maximum number of decimal degrees latitude or longitude that a 
vertex can reach out of the center of the Polygon (Default: 10)

```{r}
geo_polygon(max_radial_length = 5)
```

Within a bounding box

```{r}
geo_polygon(bbox = c(-130, 50, -120, 60))
```
